### 2018-08-26 methods.tex
Conflicts resolved (hopefully)

Liquid-fueled systems ability to continuously remove fission products and add 
fissile and/or fertile elements is the main challenge for depletion simulations. 
Introduced in this work Python-package, SaltProc, takes into account online 
separations and feeds using SERPENT 2 continuous-energy Monte Carlo neutron 
transport and depletion code.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[ht!]
        \centering
        \caption{The effective cycle times for protactinium and fission 
        products removal (reproduced from \cite{robertson_conceptual_1971}).}
        \begin{tabularx}{\textwidth}{ x | s | x }
        \hline Processing group & \qquad\qquad\qquad Nuclides & Cycle time (at 
                full power) \\ \hline Rare earths & Y, La, Ce, Pr, Nd, Pm, Sm, 
                Gd & 50 days \\ \qquad & Eu & 500 days \\ Noble metals & Se, 
                Nb, Mo, Tc, Ru, Rh, Pd, Ag, Sb, Te & 20 sec \\
        Seminoble metals & Zr, Cd, In, Sn & 200 days \\
        Gases & Kr, Xe & 20 sec \\ Volatile fluorides & Br, I & 60 days \\
        Discard & Rb, Sr, Cs, Ba & 3435 days \\ Salt discard & Th, Li, Be, F & 
                3435 days \\ Protactinium & $^{233}$Pa & 3 days \\ Higher 
                nuclides & $^{237}$Np, $^{242}$Pu & 16 years \\  \hline
        \end{tabularx}
        %\footnotetext{Chemical processing plant and gas separation system 
        %removing chemical elements (not isotopes) only. Isotopes instead of 
        %elements listed because other isotopes are short-lived and might be 
        %ignored.}
        \label{tab:reprocessing_list}
\end{table}
Th removal rates vary among nuclides in this reactor concept which dictate the 
necessary resolution of depletion calculations. If the depletion time intervals 
are very short, an enormous number of depletion steps are required to obtain 
the equilibrium composition. On the other hand, if the depletion  calculation 
time interval is too long, the impact of short-lived fission products is not 
captured. To compromise, the time interval for depletion calculations in this 
model was selected as 3 days to correlate with the removal interval of 
$^{233}$Pa and $^{232}$Th was continuously added to maintain the initial mass 
fraction of $^{232}$Th.

>>>>

The ability of liquid-fueled systems to continuously remove fission products and add 
fissile and/or fertile elements is the main challenge for depletion simulations. 
The python package introduced in this work, SaltProc, takes into account online 
separations and feeds using the SERPENT 2 continuous-energy Monte Carlo neutron 
transport and depletion code.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[ht!]
        \centering
        \caption{The effective cycle times for protactinium and fission 
        products removal (reproduced from \cite{robertson_conceptual_1971}).}
        \begin{tabularx}{\textwidth}{ x | s | x }
        \hline Processing group & \qquad\qquad\qquad Nuclides & Cycle time (at 
                full power) \\ \hline Rare earths & Y, La, Ce, Pr, Nd, Pm, Sm, 
                Gd & 50 days \\ \qquad & Eu & 500 days \\ Noble metals & Se, 
                Nb, Mo, Tc, Ru, Rh, Pd, Ag, Sb, Te & 20 sec \\
        Seminoble metals & Zr, Cd, In, Sn & 200 days \\
        Gases & Kr, Xe & 20 sec \\ Volatile fluorides & Br, I & 60 days \\
        Discard & Rb, Sr, Cs, Ba & 3435 days \\ Salt discard & Th, Li, Be, F & 
                3435 days \\ Protactinium & $^{233}$Pa & 3 days \\ Higher 
                nuclides & $^{237}$Np, $^{242}$Pu & 16 years \\  \hline
        \end{tabularx}
        \label{tab:reprocessing_list}
\end{table}
Th removal rates vary among nuclides in this reactor concept which dictate the 
necessary resolution of depletion calculations. If the depletion time intervals 
are very short, an enormous number of depletion steps are required to obtain 
the equilibrium composition. On the other hand, if the depletion  calculation 
time interval is too long, the impact of short-lived fission products is not 
captured. To compromise, the time interval for depletion calculations in this 
model was selected as 3 days to correlate with the removal interval of 
$^{233}$Pa and $^{232}$Th was continuously added to maintain the initial mass 
fraction of $^{232}$Th.
